Simulating cosmic variance in Weak Lensing: effects on parameter inferences

### 2015-11-30 Paper/paper.tex

\begin{itemize}
\item We can recycle a single $N$--body simulation to produce an ensemble of $O(10^5)$ independent maps. The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.  
\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations, but the effective dimensionality $D$, that controls the degradation of the parameter error bars, grows faster than the $O(N_b)$ that \citep{DodelsonSchneider13} predicted. 
\item The fluctuations in the $w$ forecasted variance do not exibit an appreciable trend with $N_s$ 
\end{itemize}
%
Future prospects of this work involve extending this analysis to more general feature spaces, such as the ones that characterize non--Gaussian statistics such as higher moments of $\kappa$ fields, Minkowski Functionals and higher order $\kappa$ correlators. In order to scale these considerations to future surveys such as LSST, it is necessary to see if our findinds hold when challenged by larger and higher resolution $N$--body simulations \citep{Qcontinuum}.

>>>>

\begin{itemize}
\item We can recycle a single $N$--body simulation to produce an ensemble of $O(10^5)$ independent maps. The mean feature measured from a shear ensemble, though, could be inaccurate if only one $N$--body simulation is used.  
\item The $1/N_r$ scaling for the dark energy constraint has been verified in our simulations for $N_r\gg 100$ 
\item The fluctuations in the $w$ forecasted variance do not exibit an appreciable trend with $N_s$ 
\end{itemize}
%
Future prospects of this work involve extending this analysis to more general feature spaces, such as the ones that characterize non--Gaussian statistics such as higher moments of $\kappa$ fields, Minkowski Functionals and higher order $\kappa$ correlators. In order to scale these considerations to future surveys such as LSST, it is necessary to see if our findinds hold when challenged by larger and higher resolution $N$--body simulations \citep{Qcontinuum}.
